\documentclass[12pt]{report}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[mathscr]{euscript}
\usepackage{titlesec}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{keyval}
\usepackage{subfig}
\usepackage{comment}
\usepackage{graphicx}
\usepackage{varwidth}
\usepackage{upcebumath}  
\usepackage{UPnotations}
\usepackage{hyperref}
\usepackage{rotating}
\usepackage{float}
\usepackage{gensymb}
\usepackage{mathabx}
%\usepackage{layout}
%\usepackage[hmargin={1.5in,1in},vmargin=1in,includehead,includefoot]{geometry}
\graphicspath{{images/}}

% THEOREM MACROS
%\theoremstyle{definition}
%\newtheorem{definition}{Definition}[section]
%\newtheorem{lemma}{Lemma}[section]
%\theoremstyle{theorem}
%\newtheorem{theorem}{Theorem}[section]
\newtheorem{prop}{Proposition}
\theoremstyle{definition}
\newtheorem{ex}{Example}[section]
%\theoremstyle{remark}
%\newtheorem*{remark}{Remark}
%\renewcommand\qedsymbol{$\blacksquare$}

% MATH SHORTCUTS
\makeatletter
\newcommand*\bigcdot{\mathpalette\bigcdot@{.5}}
\newcommand*\bigcdot@[2]{\mathbin{\vcenter{\hbox{\scalebox{#2}{$\m@th#1\bullet$}}}}}
\makeatother
\newcommand{\pvec}[1]{\vec{#1}\mkern2mu\vphantom{#1}}
\DeclareMathOperator{\R}{\mathbb{R}}
\DeclareMathOperator{\CC}{\mathbb{C}}
\DeclareMathOperator{\HH}{\mathbb{H}}
\newcommand{\Rx}[3]{{#1}_{#2}{(#3)}}
\newcommand{\Mr}[1]{\Rx{$M$}{#1}{\R}}
\newcommand{\Mc}[1]{\Rx{$M$}{#1}{\CC}}
\newcommand{\Mh}[1]{\Rx{$M$}{#1}{\HH}}
\newcommand{\Mf}[1]{\Rx{$M$}{#1}{$F$}}
\newcommand{\nbf}[1]{\textbf{#1}}
\newcommand{\ib}{\nbf{i}}
\newcommand{\jb}{\nbf{j}}
\newcommand{\kb}{\nbf{k}}
\newcommand{\ihat}{\hat{\ib}}
\newcommand{\jhat}{\hat{\jb}}
\newcommand{\khat}{\hat{\kb}}
\newcommand{\quat}[4]{#1 + #2\ib + #3\jb + #4\kb}
\newcommand{\ccdet}{det_{\CC}}
\newcommand{\rrdet}{det_{\R}}
\newcommand{\cdet}[1]{det_{\CC}(#1)}
\newcommand{\rdet}[1]{det_{\R}(#1)}
\newcommand{\genmatk}[4]{
	\begin{matrix}
	 #1 & \ldots & #2 \\
	 \vdots & \ddots & \vdots \\
	 #3 & \ldots & #4
	 \end{matrix}
}
\newcommand{\genmat}[1]{
	\genmatk{#1_{11}}{#1_{1n}}{#1_{n1}}{#1_{nn}}
}
\newcommand{\pgenmatk}[4]{
	\begin{pmatrix}
	 #1 & \ldots & #2 \\
	 \vdots & \ddots & \vdots \\
	 #3 & \ldots & #4
	 \end{pmatrix}
}
\newcommand{\pgenmat}[1]{
	\pgenmatk{#1_{11}}{#1_{1m}}{#1_{m1}}{#1_{mm}}
}
\newcommand{\vectC}[2]{\begin{pmatrix} #1 \\ #2 \end{pmatrix}}

% MATH ENVIRONMENT SETUP

%\setlength\arraycolsep{6pt}
%\renewcommand{\arraystretch}{0.75}
\newenvironment{proof}{\noindent \textit{Proof.}~}{\hfill$\square$}

% DOCUMENT SETUP
%\setlength{\parindent}{4em}
%\setlength{\parskip}{1em}
%\renewcommand{\baselinestretch}{2.0}
%\makeatletter
%\def\@makechapterhead#1{
%  {\parindent \z@ \raggedright \normalfont
%    \ifnum \c@secnumdepth >\m@ne
%        \huge\bfseries \@chapapp\space \thechapter
%        \par\nobreak
%        \vskip 20\p@
%    \fi
%    \interlinepenalty\@M
%    \Huge \bfseries #1\par\nobreak
%    \vskip 40\p@
%  }}
%\def\@makeschapterhead#1{
%  {\parindent \z@ \raggedright
%    \normalfont
%    \interlinepenalty\@M
%    \Huge \bfseries  #1\par\nobreak
%    \vskip 40\p@
%  }}
%\makeatother


% MAIN DOCUMENT
\begin{document}
	% DETAILS
	\title{On Quaternionic Linear Maps}

	\authorfirst{John Aaron Q.}
	\authorlast{Alcoseba}

	\degreemath{Bachelor of Science in Mathematics}
	\thesistype{Undergraduate Thesis}
	\thesisdocument{Thesis}
	\defensedate{June 3, 2017}
	\submitmonth{June}
	\submityear{2017}
	\adviser{Dr. Lorna S. Almocera}
	\reader{Dr. Natividad Estillore}
	\dept{College of Science}

	\bothabsenttrue

	%\coadviser{co-Adviser, Ph.D.}

	\dean{Jonnifer R. Sinogaya, Ph.D.} 
	\abs{This paper is an expository on \emph{Quaternionic Linear Maps} and their implications on the notion of a \emph{Quaternionic Vector Space} and \emph{Quaternionic Matrices} and their implications on the notion of a \emph{Quaternionic Determinant}. We see that different definitions have been given for the latter. We choose to look into one such definition - the \emph{Study Determinant}. We see that the Study Determinant uses homomorphisms that represent $n\times n$ \emph{Complex Matrices} as $2n \times 2n$ real matrices and homomorphisms that represent $n\times n$ \emph{Quaternionic Matrices} as $2n \times 2n$ complex matrices. }

	\acknowledge{
	This paper would not have been possible without the help of several individuals who contributed in the overall completion of this study.

	To my advisers Prof. Trilbe Lizann Espina-Vasquez and Dr. Lorna S. Almocera, for the knowledge they have shared to guide me throughout the progress of this topic all the way from conception to finalization. It is through their patience and support that I've been given enough time and freedom to work on the study as best as I possibly could.

	To Dr. Natividad Estillore, for reading and commenting on this thesis - whose suggestions and insights improved some aspects of the final manuscript.

	To my colleagues and friends, for their moral support and effort in preparing for the presentation of our study.

	To my parents and family, for the unceasing love and support they have given me for the fulfillment of this endeavour.

	Finally, to God Almighty, for always being with me especially in times of hardship and doubt until the very end.
	}

	\beforepreface
	\tableofcontents

	\newpage

	\acknowledgetrue
	\acknowledgepage

	\abstractpage
	%\listoftables
	%\listoffigures

	\afterpreface
	%main body
	\chapter{Introduction} 
	\input{chapters/chapter01}

	\chapter{Preliminaries}
	\input{chapters/chapter02}

	\chapter{Quaternionic Linear Maps}
	\input{chapters/chapter025}

	\chapter{The Study Determinant}
	\input{chapters/chapter03}

	\chapter{Summary and Recommendations}
	\input{chapters/chapter04}

	\appendix
	%\input{newfile}
	\nocite*

	\bibliographystyle{ieeetr}
	\bibliography{bibliography}
\end{document}